\section{Methods}
The present thesis is meant to give an insight into dynamics and characteristics of FAK-FAK interactions as well as interactions with a \pip{} containing membrane obtained from MD simulations. For this purpose the Martini force field and C36 were used.\\
All simulations were made with starting configurations adapted from previous work in the group (C36 forcefield: \textcite{pap003}, Martini forcefield: \textcite{SARA}). Only a FERM-kinase fragment without the FAT domain (residues 35 to 686, PDB 2J0J \autocite{structFAK}) was used. As simulation options the recommended values were used and can be found IN THE APPENDIX. All simulations have been done at a temperature of 300$\si{\kelvin}$.\\
As explained in \autoref{subsub:coarsegraining} proteins have to be stabilized in Martini with elastic networks. This was set up by \textcite{SARA} to act only inside domains with a force constant of 830 $\si{\kilo\joule\mole^{-1}\nano\meter^{-2}}$. Therefore the interface between FERM domain and kinase is not affected and the linker is still flexible.
\subsection{Free energy of \pip{} binding}
In the first part of this thesis the free energy landscape of the \pip{} binding to the basic patch was retrieved for C36, Martini and Martini with PW using umbrella sampling.\\
For simplicity only a part of the F2 subdomain was used (residues 107 to 219). The F2 was placed above a \pip{} embedded into a phosphatidylethanolamine (\pope{}) membrane (see PICTURE). The whole system was transferred to a Martini structure with a provided transformation tool \autocite{backwardpy} and the elastic network was applied.\\
After a short equilibration the protein was pulled slowly away from the membrane using a distance pull between the COM of the protein and the COM of the \pip{}. This simulation was used to retrieve starting conformations for the umbrella windows (between 90 and 120, dependent on the resulting sampling). Afterwards each umbrella window was equilibrated for 0.5$\si{\nano\second}$ and then simulated for 6$\si{\nano\second}$ (10$\si{\nano\second}$ for Martini and Martini with PW). For each forcefield the pulling and umbrella sampling was done five times to estimate the statistical error.\\
The presented results are based on a total simulation time of 6.33$\si{\micro\second}$ for Martini, 5.64$\si{\micro\second}$ for Martini with PW and 3.88$\si{\micro\second}$ for C36. % C36: 1=180, 4.2=135, 5=102, 5.2=102, 6=127, Mart: 1=134, 2=126, 3=130, 4=113, 5=130, MartPol: alle=113
\subsection{Binding pose on membrane}
Reasons, why Saras can not be.
All atom and Polarizable water.
